---
title: "Case Study 11"
author: "Betsy McCall"
date: "11/17/2020"
output:
  html_document: default
  github_document: default
---

```{r setup, include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(spData)
library(sf)

## New Packages #install
library(mapview) # new package that makes easy leaflet maps
library(foreach)
library(doParallel)
registerDoParallel(4)
getDoParWorkers() # check registered cores

# go to  http://api.census.gov/data/key_signup.html and get a key, then run the line below with your key.  Don't push your key to github!
library(tidycensus)
census_api_key(PUTKEYHERE)
##remove key from final draft
```

## Case Study #11

Making a map of Buffalo residents by race


```{r processing, echo=FALSE,message=FALSE, warning=FALSE}
racevars <- c(White = "P005003", 
              Black = "P005004", 
              Asian = "P005006", 
              Hispanic = "P004003")

options(tigris_use_cache = TRUE)
erie <- get_decennial(geography = "block", variables = racevars, 
                      state = "NY", county = "Erie County", geometry = TRUE,
                      summary_var = "P001001", cache_table=T) 

boundary <- c(xmin=-78.9,xmax=-78.85,ymin=42.888,ymax=42.92)
buffalo_crop <- st_crop(erie,boundary)

buffalo_crop$variable <- as.factor(buffalo_crop$variable)
#with assist from Ting
buffalo_par <- foreach(i=1:4, .combine='rbind',.packages=c("tidyverse","sf")) %dopar% {
  race<-levels(buffalo_crop$variable)[i]
  
  buffalo_crop %>% filter(variable==race) %>% st_sample(size=.$value) %>% st_as_sf() %>% mutate(variable=race)
}

```

## Map Plots

Is it interactive?

```{r map1, echo=TRUE, message=FALSE, as.is=TRUE, warning=FALSE}
mapview(buffalo_par,zco="variable",cex=1,lwd=0)
```

My code works just fine in an R script file, but when I try to render the HTML page, I get an error:

Error: path for html_dependency not found: 

The Web suggests it might be related to caching.I cleared the cache. No change. I got a couple missing package errors, so I installed those, and not it's just this one. I tried saving as other file types including a github document type and got a warning message about not doing that.

Not sure how to fix this.